Fail Faster

### 2025-03-20 paper/paper.tex
times not x

The runtime of \camlname generators across different input sizes is summarized in \figref{fig:time}. 
Our \camlname type-derived BST generator achieves speedups ranging from 8\% to 29.8\%, which increase 
dramatically to 515--865\% when combined with \csplitmix. The insertion-based BST generator sees 
13--21\% speedups with staging alone, and 332--435\% when also 
using \csplitmix. The single-pass BST generator benefits more significantly from 
staging, with speedups of 131--134\%, which rise to 761--795\% when combined with 
\csplitmix. We attribute the differential in performance speedup to the fact that 
BST strategies rely on relatively few calls to generator combinator functions, 
but sample extensively from the \rand; notably, single-pass BST, which uses the largest
number of calls to generator combinators, also sees the greatest benefit from staging.

For STLC, staging accounts for the bulk of performance gains, yielding
 71--164\% speedups for the type-derived STLC generator, and 360--446\% for 
 the well-typed generator. When adding \csplitmix, these numbers increase to 
 160--415\% and 383--675\%, respectively. This result makes sense because
 STLC generators, particularly the well-typed generator, sample very little from
 randomness libraries, but extensively on generator library functions.

The boolean list generator experiences 261--610\% speedups with 
staging, and its performance actually slightly \textit{decreases} when 
combined with \csplitmix (243--583\%). This is likely because sampling 
booleans is ``cheap'' enough that the overhead of crossing the FFI barrier is 
greater than that of generating values directly in OCaml.

@@

The average individual-task speedups for each strategy and benchmark are shown in 
\figref{fig:etna}, with trends in bug-finding speed closely mirroring those in performance 
from \secref{subsection:benchmarking}. The distribution of speedups in \figref{fig:swarm} reveals 
substantial variability, with most tasks clustering near the median and a long tail of outliers 
achieving much larger gains. STLC shows a more bimodal distribution of speedups
than the other benchmarks, which we attribute to the heterogenous difficulty of its tasks:  
some tasks regularly hit the 60-second timeout, while others finish in a fraction of a second. We 
find that ``easier'' tasks---those that run on the order of milliseconds---regularly achieve speedups in the 
range of 300 to 800\%, whereas tasks that run on the order of seconds achieve more moderate speedups of up to 250\%.
Overall, 
these results give strong evidence that \camlname consistently benefits bug-finding speed, sometimes drastically.
\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of all speedups---relative to BQ---for each strategy and benchmark, showing that staging leads to better bug-finding speed across the board.
  \jwc{Charts start at one? Can eliminate the BQ bar}
  }
  \label{fig:etna}
\end{figure}
\begin{figure}[h]
  \includegraphics[scale=0.35]{swarm.png}
  \caption{Swarm distribution of individual-task speedups across strategies and benchmarks---gray dots represent tasks. Plots with extremely low variance have no swarm overlay; in plots with high variance, outliers correspond to large speedups. \tr{Make mean higher-contrast.}}
  \label{fig:swarm}
\end{figure}

>>>>

The runtime of \camlname generators across different input sizes is summarized in \figref{fig:time}. 
Our \camlname type-derived BST generator achieves speedups ranging from 1.08--1.29x, which increase 
dramatically to 6.13--9.65x when combined with \csplitmix. The insertion-based BST generator sees 
1.13--1.21x speedups with staging alone, and 4.32--5.36x when also 
using \csplitmix. The single-pass BST generator benefits more significantly from 
staging, with speedups of 2.31--2.34x, which rise to 8.61--8.95x when combined with 
\csplitmix. We attribute the differential in performance speedup to the fact that 
BST strategies rely on relatively few calls to generator combinator functions, 
but sample extensively from the \rand; notably, single-pass BST, which uses the largest
number of calls to generator combinators, also sees the greatest benefit from staging.

For STLC, staging accounts for the bulk of performance gains, yielding
 1.71--2.64x speedups for the type-derived STLC generator, and 4.60--5.46x for 
 the well-typed generator. When adding \csplitmix, these numbers increase to 
 2.60--5.15x and 4.83--7.75x, respectively. This result makes sense because
 STLC generators, particularly the well-typed generator, sample very little from
 randomness libraries, but extensively on generator library functions.

The boolean list generator experiences 3.61--7.10x speedups with 
staging, and its performance actually slightly \textit{decreases} when 
combined with \csplitmix (3.43--6.83x). This is likely because sampling 
booleans is ``cheap'' enough that the overhead of crossing the FFI barrier is 
greater than that of generating values directly in OCaml.

@@

The average individual-task speedups for each strategy and benchmark are shown in 
\figref{fig:etna}, with trends in bug-finding speed closely mirroring those in performance 
from \secref{subsection:benchmarking}. The distribution of speedups in \figref{fig:swarm} reveals 
substantial variability, with most tasks clustering near the median and a long tail of outliers 
achieving much larger gains. STLC shows a more bimodal distribution of speedups
than the other benchmarks, which we attribute to the heterogenous difficulty of its tasks:  
some tasks regularly hit the 60-second timeout, while others finish in a fraction of a second. We 
find that ``easier'' tasks---those that run on the order of milliseconds---regularly achieve speedups in the 
range of 4--9X, whereas tasks that run on the order of seconds achieve more moderate speedups of up to 3.5X.
Overall, 
these results give strong evidence that \camlname consistently benefits bug-finding speed, sometimes drastically.
\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of all speedups---relative to BQ---for each strategy and benchmark, showing that staging leads to better bug-finding speed across the board.
  \jwc{Charts start at one? Can eliminate the BQ bar}
  }
  \label{fig:etna}
\end{figure}
\begin{figure}[h]
  \includegraphics[scale=0.35]{swarm.png}
  \caption{Swarm distribution of individual-task speedups across strategies and benchmarks---gray dots represent tasks. Plots with extremely low variance have no swarm overlay; in plots with high variance, outliers correspond to large speedups. \tr{Make mean higher-contrast.}}
  \label{fig:swarm}
\end{figure}
